---
title: "README"
author: "Jill MacKay"
date: "`r Sys.Date()`"
output: github_document
---


# UoEColouR
A package of University of Edinburgh branded colours



Edinburgh brand colours taken from our [Sharepoint](https://uoe.sharepoint.com/sites/Brand/SitePages/Colours.aspx). I encourage any users to thoroughly read and understand brand guidance prior to utilising Edinburgh colours.


With thanks to [Simon J's post on writing your own ggplot palette](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2).



## Examples

```{r}
library(UoEColouR)
library(ggplot2)
```

You can browse a list of the Edinburgh colours with their approximate names (I have added a precursor to all names to indicate the first palette it belongs to)

```{r}
ed_colours
```


And then you can use the `scale_uoe` function with `ggplot2`

```{r}

ggplot(aes(x = hwy, y = cty, colour = manufacturer ), data = mpg) +
  geom_point() +
  scale_colour_uoe()


ggplot(aes(x = hwy, y = cty, colour = manufacturer ), data = mpg) +
  geom_point() +
  scale_colour_uoe(palette = "muted")


ggplot(aes(x = manufacturer, fill = manufacturer), data = mpg) +
  geom_bar() +
  scale_fill_uoe()


ggplot(aes(x = manufacturer, fill = manufacturer), data = mpg) +
  geom_bar() +
  scale_fill_uoe(palette = "muted")


```
