---
title: "README"
author: "Jill MacKay"
date: "`r Sys.Date()`"
output: github_document
---


# UoEColouR
A package of University of Edinburgh branded colours



Edinburgh brand colours taken from our [Sharepoint](https://uoe.sharepoint.com/sites/Brand/SitePages/Colours.aspx). I encourage any users to thoroughly read and understand brand guidance prior to utilising Edinburgh colours. Namely, utilise these colours with great care, especially as ramping colours by specifying more than a palette's length is probably in violation of said guidelines. However, if you are producing internal reports for Edinburgh, you may find this package useful. 


With thanks to [Simon J's post on writing your own ggplot palette](https://drsimonj.svbtle.com/creating-corporate-colour-palettes-for-ggplot2) and [@jkaupp's nord package](https://github.com/jkaupp/nord) for a lot of inspiration. 

I've also [blogged about this - because I refuse to have to remember how to do any of it later](https://jillymackay.com/post/ggplot2-palettes-tutorial/).


## Install

```{r, eval = FALSE}

devtools::install_github("jillymackay/UoEColouR")

```




## Examples

```{r}
library(UoEColouR)
library(ggplot2)
```



The Edinburgh palettes are:

```{r}


uoe_show_palette("core")
uoe_show_palette("bright")
uoe_show_palette("bright-two-tone")
uoe_show_palette("muted")
uoe_show_palette("muted-two-tone")
uoe_show_palette("digital")
uoe_show_palette("recruit-ug")
uoe_show_palette("recruit-pg")
uoe_show_palette("recruit-ug-core")
uoe_show_palette("recruit-pg-core")


```


Palettes can be utilised like so:

```{r}

image(volcano, col = ed_col("bright", 20))

```



And then you can use the `scale_uoe` function with `ggplot2`:

```{r}

ggplot(aes(x = hwy, y = cty, colour = manufacturer ), data = mpg) +
  geom_point() +
  scale_colour_uoe()


ggplot(aes(x = hwy, y = cty, colour = manufacturer ), data = mpg) +
  geom_point() +
  scale_colour_uoe(palette = "muted")


ggplot(aes(x = manufacturer, fill = manufacturer), data = mpg) +
  geom_bar() +
  scale_fill_uoe()


ggplot(aes(x = manufacturer, fill = manufacturer), data = mpg) +
  geom_bar() +
  scale_fill_uoe(palette = "muted")


```
